### 2019-06-27 monograph/thesis/chapters/beautifiers.tex
Converted beautifiers.tex footnote to references.bib citation

\lang{%
    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.
}{%
    O problema é,
    mesmo que se passe por todas essas configurações,
    realizando os ajustes de preferência do usuário,
    isso levará um bom tempo.
    Infelizmente,
    você ainda está apenas configurando uma e
    talvez algumas linguagens fortemente relacionadas,
    dependendo do suporte que a ferramenta oferece.
    No caso da ferramenta \textit{Uncrustify},
    serão configurados as linguagens \textit{C},
    \textit{C++}, \textit{Java}, \textit{Pawn}\advisor{.}{,
    etc.} Para todos os outras linguagens,
    você ainda precisará encontrar outra ferramenta de formatação,
    que será certamente mais limitada\footnote{
    \url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}
    } no que ela pode customizar,
    uma vez que \textit{Uncrustify} já é uma das mais completas.
    Além disso,
    ainda precisa~=se configurar todas as novas opções já configuradas.
    Outra forte desvantagem do arquivo de configurações do \textit{Uncrustify} segue na dificuldade de entender e
    visualizar o que está sendo configurado.
    Algumas opções são claras e
    fáceis de se entender,
    já outras,
    não consegue~=se ter a mínima ideia do que elas estão fazendo e
    qual será o seu resultado final.
}

Below there are some basic formatting rules for
illustration:\footnote{\url{https://www.python.org/dev/peps/pep-0008/#should-a-line-break-before-or-after-a-binary-operator}}

\medskip
% \begin{bluebox}
\begin{enumerate}[nosep,nolistsep]
    \item Add new lines after `\{' and before `\}
    \item Add new lines before `\{'
    \item Remove empty lines
    \item Add comment lines before function
    \item Add new lines after `;'
    \item Add new lines after `\}'
    \item Remove new lines
    \item Reduce whitespace
    \item Fix bad indentation
\end{enumerate}
% \end{bluebox}
\vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

Mostly,
code formatting is recuded into this set of changes.

\section{For what is their use?}

>>>>

\lang{%
    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.
}{%
    O problema é,
    mesmo que se passe por todas essas configurações,
    realizando os ajustes de preferência do usuário,
    isso levará um bom tempo.
    Infelizmente,
    você ainda está apenas configurando uma e
    talvez algumas linguagens fortemente relacionadas,
    dependendo do suporte que a ferramenta oferece.
    No caso da ferramenta \textit{Uncrustify},
    serão configurados as linguagens \textit{C},
    \textit{C++}, \textit{Java}, \textit{Pawn}\advisor{.}{,
    etc.} Para todos os outras linguagens,
    você ainda precisará encontrar outra ferramenta de formatação,
    que será certamente mais limitada no que ela pode customizar \cite{eclisePeriodSettings},
    uma vez que \textit{Uncrustify} já é uma das mais completas.
    Além disso,
    ainda precisa~=se configurar todas as novas opções já configuradas.
    Outra forte desvantagem do arquivo de configurações do \textit{Uncrustify} segue na dificuldade de entender e
    visualizar o que está sendo configurado.
    Algumas opções são claras e
    fáceis de se entender,
    já outras,
    não consegue~=se ter a mínima ideia do que elas estão fazendo e
    qual será o seu resultado final.
}

\advisor{}{%
    \lang{%
        Below there are some basic formatting rules for illustration:

        % \begin{bluebox}
        \begin{enumerate}[nosep,nolistsep]
            \item Add new lines after `\{' and before `\}'
            \item Add new lines before `\{'
            \item Remove empty lines
            \item Add comment lines before function
            \item Add new lines after `;'
            \item Add new lines after `\}'
            \item Remove new lines
            \item Reduce whitespace
            \item Fix bad indentation
        \end{enumerate}
        % \end{bluebox}
        \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

        Mostly,
        code formatting is resumed into this set of changes.
    }{%
    }
}

\section{\lang{For what is their use?}{Qual a utilidade de Formatadores?}}

\url{https://www.python.org/dev/peps/pep-0008/#should-a-line-break-before-or-after-a-binary-operator}
